Enforced Invariant Confluence

### 2018-05-01 doc/paper/sections/evaluation.tex
Integrating Joe's feedback.

These hypotheses state that segmented \invariantconfluent{} is more performant
than linearizable replication for low-coordination workloads. But by how much?
We also aim to measure the absolute performance and scalability benefits of
segmented \invariantconfluent{} replication and how they vary as we vary the
coordination required by a workload. We perform two controlled microbenchmarks
to confirm our hypotheses and discover the absolute performance benefits. The
workloads themselves are trivial, but also not salient. \jmh{Salient to what? I'm confused by the last sentence.} Our objective is to
obtain a controlled measure of throughput and scalability as we vary workload
contention.

@@

  These results offer two insights.
  %
  First, the relationship between segmented \invariantconfluent{} and
  linearizable replication is analogous to the relationship between optimistic
  and pessimistic concurrency control protocols with coordination playing the
  role of contention \jmh{I didn't understand that last clause about ``coordination playing the role of contention.} Linearizable replication pessimistically assumes that
  concurrently executing \emph{any} pair of transactions will lead to an
  invariant violation. Thus, clients send transactions directly to a leader to
  be linearized. Conversely, segmented \invariantconfluent{} replication
  optimistically attempts to perform every transaction locally and without
  coordination. A server only initiates a round of coordination if it is found
  to be necessary. As a consequence, segmented \invariantconfluent{}
  replication can offer substantial performance benefits over linearizable
  replication for low-coordination workloads, but is inferior for medium to
  high contention workloads. \jmh{say why}

@@

\begin{benchmark}
\jmh{Can you get the figures to color ``eventual'' and ``linearizable'' the same in both?}
  In this benchmark, we measure the scale-out of segmented
  \invariantconfluent{} replication. We repeat \benchref{VaryWithdraws} while
  we vary the number of servers that we use to replicate our object. When we
  replicate with $n$ servers, we use $3n$ clients (the $3$ colocated clients on
  each server) as part of the workload. The results are shown in
  \figref{VaryNodes}.

>>>>

These hypotheses state that segmented \invariantconfluent{} is more performant
than linearizable replication for low-coordination workloads. But by how much?
We also aim to measure the absolute performance and scalability benefits of
segmented \invariantconfluent{} replication and how they vary as we vary the
coordination required by a workload. We perform two controlled microbenchmarks
to confirm our hypotheses and discover the absolute performance benefits. The
workloads themselves are trivial but are not the focus of our experiments. Our objective is to
obtain a controlled measure of throughput and scalability as we vary workload
contention.

@@

  These results offer two insights.
  %
  First, the relationship between segmented \invariantconfluent{} and
  linearizable replication is analogous to the relationship between optimistic
  and pessimistic concurrency control protocols. Linearizable replication pessimistically assumes that
  concurrently executing \emph{any} pair of transactions will lead to an
  invariant violation. Thus, clients send transactions directly to a leader to
  be linearized. Conversely, segmented \invariantconfluent{} replication
  optimistically attempts to perform every transaction locally and without
  coordination. A server only initiates a round of coordination if it is found
  to be necessary. As a consequence, segmented \invariantconfluent{}
  replication can offer substantial performance benefits over linearizable
  replication for low-coordination workloads. However, it is inferior for
  medium to high contention workloads because the majority of transactions that
  are sent to a server are eventually aborted and relayed to the leader. This
  additional latency is avoided by linearizable replication which sends
  transactions directly to the leader.

@@

\begin{benchmark}
  In this benchmark, we measure the scale-out of segmented
  \invariantconfluent{} replication. We repeat \benchref{VaryWithdraws} while
  we vary the number of servers that we use to replicate our object. When we
  replicate with $n$ servers, we use $3n$ clients (the $3$ colocated clients on
  each server) as part of the workload. The results are shown in
  \figref{VaryNodes}.
